Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2017-10-25 fully-abstract-comp/prisc-extended-abstract/linear-well-bracketed-control.tex
Address remarks by Lau and Lars in PriSC extended abstract.

\section{Formalising well-bracketed control flow}
The second improvement we are making is related to the properties of well-bracketed control flow and local state encapsulation.
Our previous work did not actually have a precise statement of these properties.
We only show a reasoning technique that can be used to prove certain example programs that rely on the properties.
Although it can be argued that this proof technique should perhaps qualify as a formal statement of the properties, we are investigating an alternative approach, based on the notion of fully abstract compilation \citep{abadi_protection_1999}.

We intend to start from a formalisation of an assembly language for a capability machine with linear capabilities (the target language).
Our idea is then to introduce a variant of this target language that features a primitive stack, built into the operational semantics, as well as additional instructions like call and return.
While the original target language is a standard assembly language without even the notion of a stack, this variant language (the source language) does have a stack, and control flow well-bracketedness and local state encapsulation are evident properties of the operational semantics.
We can formalise our calling convention in the definition of a compiler from the source language to the target language.
Additionally, we conjecture that this compiler can be proved fully abstract, thus formally expressing and establishing security of the calling convention.

>>>>

\section{Formalising well-bracketed control flow}
The second improvement we are making is related to the properties of well-bracketed control flow and local state encapsulation.
To establish these properties, our previous work followed the approach taken by previous work in other settings \citep{dreyer_impact_2010}: we provide a sound reasoning technique and use it to prove soundness of challenging example programs that rely on the properties.
In the current work, we are investigating an alternative way to formalise the two properties, based on the notion of fully abstract compilation \citep{abadi_protection_1999}.

We intend to start from a formalisation of an assembly language for a capability machine with linear capabilities (the target language).
Our idea is then to introduce a variant of this target language that features a primitive stack, built into the operational semantics, as well as additional instructions like call.
While the original target language is a standard assembly language without even the notion of a stack, this variant language (the source language) does have a stack, and control flow well-bracketedness and local state encapsulation follow more directly from the operational semantics.
We can formalise our calling convention in the definition of a compiler from the source language to the target language.
Additionally, we conjecture that this compiler can be proved fully abstract, thus formally expressing and establishing security of the calling convention.
